### 2008-05-16 trunk/Papers/dl-gre-08/gre.tex
Changed a sentence in the conclusions to put it in line with the change at the end  of section 3.1

Notice that we presented both algorithms as first refining $\RE$  according to the
propositional symbols, and then by relational expressions of
increasing depth. But propositional symbols can easily be encoded by means of new relation symbols (e.g., we could represent that $f_1$ is a flower in Fig.~\ref{fig:dale-haddock} as a reflexive loop labeled  $\mathsf{flower}$). By means of this encoding, any arbitrary ordering of preference can be used when generating $\RE$, and we don't need to distinguish between propositions and relations.

>>>>

We presented both algorithms as first refining $\RE$
according to propositional symbols, and then by relational
expressions of increasing depth. But, actually, propositional symbols can be encoded using new relational symbols (e.g., we could represent
that $f_1$ is a flower in Fig.~\ref{fig:dale-haddock} as a relation labeled $\mathsf{flower}$ from $f_1$ to an additional dummy element $d$).
In this way, any
arbitrary ordering of preference can be used when generating $\RE$,
and we don't need to distinguish between propositions and relations.
